---
title: "Measurement of Error"
author: "Siyu Sun"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## Simplest Case

Absolute error: $|x - \widehat{x}|$  

But cannot address difference importance of differences in relation to x, thus 
Relative error:  

$\frac{|x - \widehat{x}|}{|x|}$

For computing convenience, avoid the case x can be non-zero:  

$\frac{|x - \widehat{x}|}{1 + |x|}$

has the property that when $|x|>>1$, similar to relative error; and when 
$|x| <= 1$, similar to absolute error.

### Plots

```{r plot1, fig.height = 4, fig.width  = 6}
x <- seq(0, 100, 0.1)
x_e <- x + rnorm(length(x))
par(mfrow = c(2,2), mar = c(1,2,1,1))
plot(x)
lines(x_e)
plot(abs(x-x_e), type="l")
plot(abs(x-x_e)/abs(x), type="l")
plot(abs(x-x_e)/(1+abs(x)), type="l")

```


## Log.

The function that outputs between 0 and 1.


```{r plot2, fig.height = 4, fig.width  = 6}
x1 <- seq(0, 1, 0.01)
x2 <- seq(0, 100, 0.1)
y1 <- exp(x1) / (1 + exp(x1))
y2 <- exp(x2) / (1 + exp(x2))
par(mfrow = c(2,2), mar = c(1,2,1,1))
plot(x1, y1)
plot(x2, y2)
plot(log(x1), y1)
plot(log(x2), y2)

```

